\documentclass[11pt]{article}

% NOTE: The "Edit" sections are changed for each assignment

% Edit these commands for each assignment

\newcommand{\assignmentduedate}{October 17}
\newcommand{\assignmentassignedate}{October 3}
\newcommand{\assignmentnumber}{Four}

\newcommand{\labyear}{2017}
\newcommand{\labday}{Tuesday}
\newcommand{\labtime}{2:30 pm}

\newcommand{\assigneddate}{Assigned: \labday, \assignmentassignedate, \labyear{} at \labtime{}}
\newcommand{\duedate}{Due: \labday, \assignmentduedate, \labyear{} at \labtime{}}

% Edit these commands to give the name to the main program

\newcommand{\mainprogram}{\lstinline{generator.py}}
\newcommand{\mainprogramsource}{\lstinline{generator/generator.py}}
\newcommand{\maintestsource}{\lstinline{generator/tests/test_generator.py}}

% Edit this commands to describe key deliverables

\newcommand{\reflection}{\lstinline{README.md}}

% Commands to describe key git tasks

\newcommand{\gitcommitfile}[1]{\command{git commit #1}}
\newcommand{\gitaddfile}[1]{\command{git add #1}}

\newcommand{\gitadd}{\command{git add}}
\newcommand{\gitcommit}{\command{git commit}}
\newcommand{\gitpush}{\command{git push}}
\newcommand{\gitpull}{\command{git pull}}

% Use this when displaying a new command

\newcommand{\command}[1]{``\lstinline{#1}''}
\newcommand{\program}[1]{\lstinline{#1}}
\newcommand{\url}[1]{\lstinline{#1}}
\newcommand{\channel}[1]{\lstinline{#1}}
\newcommand{\option}[1]{``{#1}''}
\newcommand{\step}[1]{``{#1}''}

\usepackage{pifont}
\newcommand{\checkmark}{\ding{51}}
\newcommand{\naughtmark}{\ding{55}}

\usepackage{listings}
\lstset{
  basicstyle=\small\ttfamily,
  columns=flexible,
  breaklines=true
}

\usepackage{fancyhdr}

\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}

\pagestyle{fancy}

\fancyhf{}
\rhead{Computer Science 280}
\lhead{Laboratory Assignment \assignmentnumber{}}
\rfoot{Page \thepage}
\lfoot{\duedate}

\usepackage{titlesec}
\titlespacing\section{0pt}{6pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

\newcommand{\labtitle}[1]
{
  \begin{center}
    \begin{center}
      \bf
      CMPSC 280\\Software Engineering\\
      Fall 2017\\
      \medskip
    \end{center}
    \bf
    #1
  \end{center}
}

\begin{document}

\thispagestyle{empty}

\labtitle{Laboratory \assignmentnumber{} \\ \assigneddate{} \\ \duedate{}}

\section*{Objectives}

The focus of this assignment is on applying effective project management and team work strategies to enhance an existing
open-source project that is available on GitHub. Using GitHub and the ``GitHub flow'' model, you will work in an
assigned team to specify, design, implement, test, document, and release a fully functioning programming systems product
that can be deployed into immediate use. For this laboratory assignment, your team will work with the other teams in the
class to collaboratively complete all of the features requested by the on-site customer.

\section*{Suggestions for Success}

\begin{itemize}
  \setlength{\itemsep}{0pt}

\item {\bf Use the laboratory computers}. The computers in this laboratory feature specialized software for completing
  this course's laboratory  assignments. If it is necessary for you to work on a different machine, be sure to regularly
  transfer your work to a laboratory machine so that you can check its correctness. If you cannot use a laboratory
  computer and you need help with the configuration of your own laptop, then please carefully explain its setup to the
  systems administrator or the course instructor when you are asking questions.

\item {\bf Follow each step carefully}. Slowly read each sentence in the assignment sheet, making sure that you
  precisely follow each instruction. Take notes about each step that you attempt, recording your questions and ideas and
  the challenges that you faced. If you are stuck, then please tell the course instructor what assignment step you
  most recently completed.

\item {\bf Regularly ask and answer questions}. Please log into Slack at the start of a laboratory session and then join
  the appropriate channel. If you have a question about one of the steps in an assignment, then you can post it to the
  designated channel. Or, you can ask one of your team members or talk with course instructor in person or through
  Slack.

\item {\bf Store all your deliverables in GitHub}. As in past laboratory assignments, you will be responsible for
  storing all of your files (e.g., Python source code and Markdown-based writing) in a Git repository using GitHub and
  GitHub Classroom. Please verify that you have saved your source code in your Git repository by using \command{git
  status} to ensure that everything is updated. You can see if your assignment submission meets the established
  correctness requirements by using the provided checking tools on your local computer and in checking the commits in
  GitHub. Additionally, your team should perform all project management and communication tasks through GitHub. That is,
  all discussions about your programming systems product and the source code of and documentation for it must be
  available in GitHub.

\item {\bf Keep all of your files}. Don't delete your programs, output files, and written reports after you submit them
  through GitHub; you will need them again when you study for the quizzes and examinations and work on the other
  laboratory and final project assignments.

\item {\bf Back up your files regularly}. All of your files are regularly backed-up to the servers in the Department of
  Computer Science and, if you commit your files regularly, stored on GitHub. However, you may want to use a flash
  drive, Google Drive, or your favorite backup method to keep an extra copy of your files on reserve. In the event of
  any type of system failure, you are responsible for ensuring that you have access to a recent backup copy of all your
  files.

\item {\bf Hone your technical writing skills}. Computer science assignments require to you write technical
  documentation and descriptions of your experiences when completing each task. Take extra care to ensure that your
  writing is interesting and both grammatically and technically correct, remembering that computer scientists must
  effectively communicate and collaborate with their team members and the tutors, teaching assistants, and course
  instructor.

\item {\bf Review the Honor Code on the syllabus}. While you may discuss your assignments with others, copying source
  code or writing is a violation of Allegheny College's Honor Code.

\end{itemize}

\vspace*{-1em}

\section*{Reading Assignment}

If you have not done so already, please read all of the relevant ``GitHub Guides'', available at
\url{https://guides.github.com/}, that explain how to use many of the features that GitHub provides. In particular,
please make sure that you have read guides such as ``Mastering Markdown'' and ``Documenting Your Projects on GitHub'';
each of them will help you to understand how to use both GitHub and GitHub Classroom. To do well on this assignment, you
should review Chapters 1 and 2 of the SETP textbook. You should also read Chapter 3 and 4 of SETP, paying particularly
close attention to the content about strategies for project management and requirements elicitation. To ensure that your
team understands what kind of product it must collaboratively implement, please review Chapter 1 in MMM, focusing on the
definition of a programming systems product. Finally, you and your team members should read and discuss the content on
these web sites:

\vspace*{-.5em}

\begin{itemize}
  \setlength{\itemsep}{0pt}
  \item \url{https://guides.github.com/introduction/flow/}
  \item \url{https://help.github.com/articles/github-flow/}
  \item \url{https://help.github.com/categories/collaborating-with-issues-and-pull-requests/}
\end{itemize}

\vspace*{-1em}

\section*{Organizing Your Software Development Team}

You should organize yourselves into the teams given in the \channel{\#announcements} channel in our Slack team. After
reviewing the reading assignments mention in the previous section and discussing the software that you are invited to
implement for this assignment, your team should discuss how it will complete this project's tasks. As you are making
task assignments, please think about the unique skillset of each member of your development team. When it seems as
though there are no team members who best fit certain roles, you should make compromises to ensure that all work will
still be successfully finished. Your assignment of people to roles should ensure that individuals have the opportunity
to explore new tasks and learn more about many software engineering tasks.

Importantly, your team must complete this assignment in conjunction with the other teams in this class. As such, it is a
good idea for your project manager to coordinate with the other project managers to decide the best way to allocate
tasks to the separate teams and team members. While it is up to the class to decide, it also may be a good idea for the
teams to identify several project managers who will agree to coordinate this project and approve all of the pull
requests. Remember, it is important for the project managers to ensure that all of their members know how to effectively
use GitHub and then make a plan for how you will control your source code and documentation and communication using
GitHub features like the issue tracker, commit log, and pull requests. Students who do not know how to use these
features of GitHub should immediately schedule a meeting with the course instructor and ask their project manager any
questions about this matter. Remember, your grade for this assignment is a function of the work that you completed and
documented through the main project's GitHub repository and reported on in your private repository's \reflection{}.
Please see the instructor if you do not understand this grading strategy.

\section*{Accessing the Laboratory Assignment on GitHub}

To access the laboratory assignment, you should go into the \channel{\#announcements} channel in our Slack team and find
the announcement that provides a link for it. Copy this link and paste it into your web browser. Now, you should accept
the laboratory assignment and see that GitHub Classroom created a new GitHub repository for you to access the
assignment's starting materials and to store the completed version of your assignment. Specifically, to access your new
GitHub repository for this assignment, please click the green ``Accept'' button and then click the link that is prefaced
with the label ``Your assignment has been created here''. If you accepted the assignment and correctly followed these
steps, you should have created a GitHub repository with a name like
``Allegheny-Computer-Science-280-Fall-2017/computer-science-280-fall-2017-lab-4-gkapfham''. Unless you provide the
instructor with documentation of the extenuating circumstances that you are facing, not accepting the assignment means
that you automatically receive a failing grade for it.

You will use this GitHub repository to obtain a link to the GitHub project that you will enhance for this assignment.
Notably, the course instructor will give add you as a collaborator to the GitHub repository for this assignment once you
have accepted the assigned in the \channel{\#announcements} channel and you have uploaded a professional profile picture
to GitHub. You will also use the \reflection{} file in this repository to report on all of the work that you completed
and review the work that your team and class members completed. Specifically, you should use the \reflection{} file to
evaluate the effectiveness of your team and the other teams, commenting on who completed what work and how well the work
was completed. Considering the definitions given in MMM, you should also assess the quality of the programming systems
product that the class completed by the deadline.

As in past assignments, you can click the ``Clone or download'' button and, after ensuring that you have selected
``Clone with SSH'', please copy this command to your clipboard. To enter your course directory you should now type
\command{cd cs280F2017}. By typing \command{git clone} in your terminal and then pasting in the string that you copied
from the GitHub site you will download all of the code for this assignment. Before starting the assignment, make sure
that each of your team members has access to their own private repository and they understand what type of content they
should include in the \reflection{} file. Please see the instructor with questions about this step.

\section*{Collaborating With Your Software Development Team}

Your team should review the GitHub issue tracker for a description of each of the key tasks that you need to complete
for this project. Attempting to manage risk and estimate the effort required for individual team members to resolve
these issues, you should now assign people to roles and tasks. While it is acceptable for you to have in-person
discussions with your team members, please remember that all important discussions and decisions must be documented in
GitHub. Finally, don't forget that you are completing this assignment in conjunction with the other teams in the course
--- the class should consider identifying project managers who will coordinate this project.

Your team should work with the customer to prioritize the implementation of the issues currently raised in the project's
issue tracker. When you are not sure how to implement a requirement, then you must clarify the matter with the customer
and with the other members of the team. Don't forget that your work will be evaluated according to the standards
established on the final page of this assignment sheet. Please see the instructor if you do not know how to
effectively collaborate.

Since each team member is an administrator the project's GitHub repository, everyone can create ``branches'' allocated
to, for instance, each of the program features that you want to implement or the documentation that you want to write.
Once a specific branch contains the finished version of its associated deliverable, a team member should create a pull
request for discussion. If a project manager judges that the pull request has all of the expected characteristics, then
it should be merged into the ``master'' branch of your repository. If the pull request is not accepted, then the team
member should improve it until it meets everyone's expectations. Your team should continue to use this model, called
``GitHub flow'', to support the completion of all deliverables.

\section*{Summary of the Required Deliverables}

\noindent Students do not need to submit printed source code or technical writing for any assignment in this course.
Instead, this assignment invites you to submit, using GitHub, the following deliverables.

\begin{enumerate}

\setlength{\itemsep}{0in}

\item Stored in \reflection{}, a reflection on your contributions to the group project and the contributions made by
  your team members and the other members of this class. Refer to the relevant sections of this sheet for details about
  what to write in your repository's \reflection{} file.

\item A properly documented, well-formatted, and correct version of all of the source code needed to fulfill the
  requirements given in the issue tracker of the GitHub repository for this project.

\item Stored in the \reflection{} file of the project's GitHub repository, user documentation that handles all of the
  issues raised in the issue tracker of the GitHub repository for this project.

\end{enumerate}

\vspace*{-1em}

\section*{Evaluation of Your Laboratory Assignment}

Using a report that the instructor shares with you through the commit log in GitHub, you will privately received a grade
on this assignment and feedback on your deliverables. The instructor will also evaluate the effectiveness with which the
teams and the class completed the assignment.

% Your grade for the assignment will be a function of the whether or not it was submitted in a timely fashion. Other
% factors will also influence your final grade on the assignment. In addition to studying the efficiency and effectiveness
% of your Python source code, the instructor will also evaluate the accuracy of both your technical writing and the
% comments in your source code.

The instructor will assess team effectiveness as {\bf excellent} when all of these standards are met:

\vspace*{-.5em}

\begin{enumerate}
  \setlength{\itemsep}{0pt}

  \item All team members regularly contribute, in a timely fashion, to the GitHub project through the issue tracker,
    pull requests, and the committing of source code and documentation.

  \item All team members contribute correct, useful Python source code and/or Markdown documentation that supports the
    creation of a working and valuable programming systems product.

  \item All team members participate in the classroom discussions, sharing status updates and ideas.

  \item All team members regularly communicate with others in a respectful and informative manner.

  \item All team members work with others and the instructor to resolve any differences that arise.

\end{enumerate}

\vspace*{-.5em}

The instructor will assess team effectiveness as {\bf good} when the majority of the team members fulfill the
aforementioned standards. The team's effectiveness will be assessed as {\bf average} when some, but not the majority, of
the team members make meaningful contributions to the project, according to these set standards. The course instructor
will assess team effectiveness as {\bf below average} when, as a whole, the team does not function according to the
above standards.

The instructor will assess product quality as {\bf excellent} when, by the established deadline, the product's GitHub
repository contains a full programming systems product that contains: clear and useful documentation, a comprehensive
and passing test suite that effectively covers the code base, and correct implementations of all, or the majority of,
the requirements listed in the issue tracker. The instructor will assess product quality as {\bf good} when all of the
aforementioned standards are met, but some of the requirements are not fully implemented or not implemented correctly.
The product's quality will be assessed as {\bf average} when some, but not the majority, of the requirements are
properly fulfilled. The course instructor will assess product quality as {\bf below average} when, as a whole, the
product does not feature new requirements or there is a regression in functionality.

Every student will receive the same baseline grade for team effectiveness and product quality. However, an individual
student grade will be adjusted higher or lower according to their contribution's to the project, as reflected in the
material that they and others include in the \reflection{} file of the private GitHub repository and in the public
repository of the project's GitHub repository.

\end{document}
